Accelerated evolution of convective simulations

### 2018-02-23 tex/bvp_paper.tex
overhaul of conclusionss

In this work, we study a method of achieving accelerated evolution of a
convective simulation through adjusting the thermodynamic state using information 
from resolved, convective dynamics. We couple measurements of the (non-converged)
convective solution with knowledge about energy balances in the eventual solution
to self-consistently adjust the mean thermodynamic profile towards its final state. 
While such a method has been used previously \cite{hurlburt&all1986}, 
we find no explanation in the current literature of the steps involved in employing
this method, nor any study into the accuracy of such a method.
In section \ref{sec:experiment}, we describe our convective simulations, our
numerical methods, and our method for achieving accelerated evolution. In
section \ref{sec:results}, we compare solutions reached through the accelerated evolution
method to those that have been evolved through a full diffusive timescale, and we
examine select simulations at very high Ra which have achieved accelerated evolution. Finally,
in section \ref{sec:extensions}, we discuss extensions of the methods presented here,
and we offer concluding remarks in section \ref{sec:conclusion}.

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/time_trace.png}
\caption{Traces of kinetic energy and mean temperature vs. time for a (a) SE and (b)
AE run are shown at $S = 10^5$.
The horizontal extent of the plots is set
such that one simulation time unit takes up an equal amount of paper space in (a) and (b).
The mean evolved values are shown as horizontal dashed lines.
(c) System fluxes shortly after the convective transient are shown, at times corresponding
to the orange highlighting in (a) and (b).  The sum of the flux is shown in black,
the convective flux is shown in purple, and the conductive flux is shown in red.
(d) Fluxes in the evolved AE state are shown, measured during the time highlighted
in green in (b).  
(e) The difference between the AE and SE fluxes, measured over the green highlighted
regions in (a) and (b), are shown.
Note that the black dashed vertical line in (a) denotes the simulation time at which
averaging begins for the AE solution shown in (b).
\label{fig:time_trace} }
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
\caption{Volume- and time-averaged measurements for AE runs are shown in (a)-(c).
Symbols are located at the mean value of
each measurement, while vertical lines represent the standard deviation of the measurement,
showing natural variation over the
averaging window, and error bars represent the change in the mean value over the window,
such that large error bars would represent a poorly converged solution.
(a) The Nusselt number scales as $Ra^{1/5}$, and above S$\geq 10^{3+2/3}$,
simulations exhibit oscillating plume structures whose heat transport varies over time.  
(b) The RMS Reynolds number, which measures the level of turbulence in the evolved solution, scales as
Ra$^{0.45}$. (c) Temperature, with its value at the upper boundary removed, is shown.
Relative error for (d) Nu, (e) Re, and (f) $T$ are shown between measurements 
taken in AE solutions and SE solutions.
The greyed area of the plot indicates the region in which only AE runs were
carried out due to computational expense. The run at $S = 10^5$ marked as a
black square is examined in more details in Figs. \ref{fig:time_trace},
\ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison}.
\label{fig:parameter_space_comparison} }
\end{figure}

@@

As the AE method primarily serves to adjust the thermodynamic structure of the
solution, we compare the temperature profile attained by AE and SE in 
Fig. \ref{fig:temp_comparison}.  We see that the boundary layer length scale is 
nearly identical in the AE and SE solution (Fig. \ref{fig:temp_comparison}a), but that
the mean temperature in the interior differs by about 0.5\% on average
(Fig. \ref{fig:temp_comparison}b). The probability distribution function of point-by-point
temperature values are compared in Fig. \ref{fig:temp_comparison}c.  We construct
this PDF by interpolating our temperature field onto a regular grid, determing the
frequency distribution of all $T$ values, and then properly normalizing such that
the integral of the PDF is unity.  In addition to the
difference in mode which can be seen in the mean vertical profile, the SE case
has a broader spread of temperature values.  This can likely be attributed to the
slight overstabilization of the temperature profile obtained by the AE method
(as can be seen in Fig. \ref{fig:time_trace}a\&b).  One means of comparing two
probability distributions to determine if they are drawn from the same underlying
sample is through the use of a Kolmogorov-Smirnov (KS) \cite{wall&jenkins2012}.
In general, a KS test must be conducted on independent, uncorrelated data, which
poorly describes the point-by-point values of flow in a fluid simulation. Thus,
we will merely use the KS statistic, the maximum difference
between the cumulative distribution functions (CDFs) of the two sample distributions,
as a numerical method of directly comparing the two PDFs.  For the distributions
shown in Fig. \ref{fig:temp_comparison}c,
we find a KS statistic of 0.185 near the modes, which is large, and implies that
these two distributions are different.

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/temp_comparison.png}
\caption{Comparisons of the evolved thermodynamic states of an AE and SE run
at $S = 10^{5}$ are shown.  (a) Evolved temperature profiles, as a function of height.
(b) The percentage difference between the temperature profiles as a function of height.
(c) Probability distributions of point-by-point measurements of the temperature field.
$T$ is sampled every 0.1 time units for 500 total time units,
and was interpolated onto an evenly spaced grid before sampling.
The cumulative distribution function is overplotted on each plot. 
\label{fig:temp_comparison} }
\end{figure}

@@

\section{Extensions \& Conclusion}
\label{sec:extensions}
In this work we have used \RB convection as a test case for the AE method, but we argue that
the true power of this method is in its extensions to more complicated studies.
Such extensions are beyond the scope of this paper, but we will briefly describe
areas in which extensions to the AE method should be explored.
We note that a strength of the AE method is its generality.  One
need only derive the steady-state, horizontally-averaged equations for a given
equation set (e.g., Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}))
and couple that information with knowledge of the current dynamics (Eqn. (\ref{eqn:bvp_ratios}))
and the boundary conditions. Thus this method can be easily applied to more complex
systems, so long as the experimenter understand the energy transport
present in their systems.

In studies of stratified convection where the thermal diffusivity
is inversely proportional to the density \cite{anders&brown2017}, the
thermal timescale deep in the atmosphere is much larger than the timescale
near the surface.  Thus, the AE method can be a very important tool for studying
highly stratified systems which aim to model realistic astrophysical atmospheres.
Through carefully examining the flux in excess of the flux conducted along the
adiabatic temperature gradient, the fractions of Eqn. (\ref{eqn:bvp_ratios})
can be constructed for such a system.  In addition to solving for the average
hydrostatic balance and thermal equilibrium, it is essential to simultaneously
ensure that mass is conserved in truly stratified systems by adding a 
mass-conservation equation, similar to those used in stellar structure models
\cite{paxton&all2011}.

It is common for studies to pair stable and convecting regions
\cite{hurlburt&all1986, brandenburg&all2005, couston&all2017}.
In such studies, particularly when the interface between the stable region
and the convecting region is stiff and motions do not penetrate from the convecting
region into the stable region, the stable region cannot rely on convective
motions to assist in the restratification of the thermal profile.
In fully-convective domains, such as those studied here, the atmosphere evolves
much more rapidly than the thermal diffusion time (see e.g., Fig. \ref{fig:time_trace}a,
where the SE solution is essentially fully converged after $4\cdot 10^3$ frefall units
despite the thermal timescale being roughly $10^4$ frefall units).

We have only studied solutions in which we use mixed thermal boundary conditions,
as in Eqn. \ref{eqn:bcs}. However, this method can be easily applied to fixed-temperature
boundary conditions, as well.  Rather than knowing the total final flux (F$_{\text{bot}}$)
through the system a priori, it must be measured using the ratios in
Eqn. \ref{eqn:bvp_ratios}.  The integrated conductive flux is known in these systems exactly thanks 
to the fixed temperature jump across the domain.  The total flux through the system
($F_{\text{bot}}$) can is thus $\mathcal{P} / \int f_{\text{cond}} dz$ (double-check).
We hesitate to use the AE method for systems in which
both boundaries fix the flux, as such systems have degenerate solutions for the temperature.

In conclusion, here we have described a method for converging convective simulations using
a method of Accelerated Evolution (AE), and compared it to Standard
Evolution (SE) achieved by running simulations for a thermal timescale.
We have shown that the AE method produces dynamics that are similar to SE
dynamics on much shorter timescales, and have discussed differences that arise
between the two methods.

We have shown that the AE method is valid at low values of $S$, in which solutions
converge quickly, and at high values of $S$, at which SE solutions can take an
intractable amount of time.  This shows that the AE method not only progresses
solutions towards the correct evolved state (at high $S$), but it also does not
throw the simulation out of the correct evolved state (at low $S$).  We have studied
the AE method in both 2D and 3D, but since the method relies fundamentally on
1D information from the transient flows, we have restricted most of our study
to 2D and merely demonstrated the method's efficacy in 3D, too.

This work serves as a first step towards creating robust methods for
achieving evolved convective solutions at high Ra on short timescales.
Future studies will extend this method to stratified, fully compressible
convection \cite{anders&brown2017}, and to systems with internal heating.

@@

\appendix
\section{Accelerated Evolution Recipe}
\label{appendix:recipe}
In order to achieve Accelerated Evolution (AE), we solve a 1D Boundary Value Problem
consisting of Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}).
There are a steps required to properly advance the solution are as follows:
\begin{enumerate}
\item Update averages of $F_{\text{conv}}$, $F_{\text{tot}}$, and $\angles{\bm{u} \times \bm{\omega}}$
every timestep.  Wait until that average converges. To ensure that an average is converged, at
least some time $t_{\text{min}}$ must have passed since the average was started, and
the profiles must change by no more than $P$\% on a given timestep.
\item Construct F$_\text{conv, ev}$ and $\xi$ as specified in section \ref{subsection:ae}.
\item Solve for $\angles{T_1}_{x,y}$ and $\angles{\varpi}_{x,y}$ of the
evolved state.  Adjust the profiles in the convecting simulation accordingly
\item Multiply the velocity field and the fluctuations in $T - \angles{T}_{x,y}$ by $\sqrt{\xi}$ in the IVP. 
\item Continue running the simulation.
\end{enumerate}
We refer to this process as an ``AE BVP solve.''

In general, we find that repeating this method multiple times is the best way to
ensure that the AE solution is truly converged. For all runs in 2D at $S < 10^5$, we
waited for 50 time units after peak transient, completed an AE BVP solve
with $t_{\text{min}} = 30$ and $P = 0.1$, waited 50 more time units, and then
did a second AE BVP solve with the same parameters.
For all 3D runs and 2D runs in the range $S \in [10^5, 10^6]$,
we waited 20 time units after peak transient, completed an AE BVP solve
with $t_{\text{min}} = 20$ and $P = 1$ in order to quickly reach a near-
converged state and vastly increase our timestep.  After this, we completed
two AE BVP solves, separated by 30 time units each, with $t_{\text{min}} = 30$
and $P = 0.1$ to get very close to the solution (as in Fig. \ref{fig:time_trace}b).
At very high $S = 10^7$, we ran two AE BVP solves with $t_{\text{min}} = 20$ and
$P = 1$, waiting 20 time units after peak transient and 30 time units between
the two solves.

\section{Table of Runs}
\label{appendix:run_table}
\begin{center}
\begin{tabularx}{\textwidth}{ X X X X X X X X X }
\hline															
$S$	&	Ra	&	nz	&	nx, ny	&	$t_{\text{therm}}$	&	$t_{\text{avg}}$	&	Nu$_{\text{SE}}$	&	Nu$_{\text{AE}}$	\\
\hline															
$10^{1/3}$	&	$2.79 \cdot 10^3$	&	32	&	64	&	$52.8$	&	100	&	1.46	&	1.46	\\
$10^{2/3}$	&	$6.01 \cdot 10^3$	&	32	&	64	&	$77.6$	&	100	&	1.95	&	1.95	\\
$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64	&	$114$	&	100	&	2.43	&	2.42	\\
$10^{1 + 1/3}$	&	$2.79 \cdot 10^4$	&	32	&	64	&	$167$	&	100	&	2.54	&	2.54	\\
$10^{1 + 2/3}$	&	$6.01 \cdot 10^4$	&	32	&	64	&	$245$	&	100	&	3.14	&	3.14	\\
$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128	&	$360$	&	100	&	3.8	&	3.8	\\
$10^{2 + 1/3}$	&	$2.79 \cdot 10^5$	&	64	&	128	&	$528$	&	100	&	4.71	&	4.71	\\
$10^{2 + 2/3}$	&	$6.01 \cdot 10^5$	&	64	&	128	&	$776$	&	100	&	5.5	&	5.5	\\
$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256	&	$1.14 \cdot 10^3$	&	200	&	6.4	&	6.33	\\
$10^{3 + 1/3}$	&	$2.79 \cdot 10^6$	&	128	&	256	&	$1.67 \cdot 10^3$	&	500	&	6.87	&	6.95	\\
$10^{3 + 2/3}$	&	$6.01 \cdot 10^6$	&	256	&	512	&	$2.45 \cdot 10^3$	&	500	&	7.54	&	7.59	\\
$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512	&	$3.60 \cdot 10^3$	&	500	&	8.83	&	8.83	\\
$10^{4 + 1/3}$	&	$2.79 \cdot 10^7$	&	256	&	512	&	$5.28 \cdot 10^3$	&	500	&	10.13	&	10.14	\\
$10^{4 + 2/3}$	&	$6.01 \cdot 10^7$	&	256	&	512	&	$7.76 \cdot 10^3$	&	500	&	11.65	&	11.69	\\
$10^5$	&	$1.30 \cdot 10^8$	&	512	&	1024	&	$1.14 \cdot 10^4$	&	500	&	14.02	&	14.18	\\
$10^{5 + 1/3}$	&	$2.79 \cdot 10^8$	&	512	&	1024	&	$1.67 \cdot 10^4$	&	500	&	--	&	16.21	\\
$10^{5 + 2/3}$	&	$6.01 \cdot 10^8$	&	512	&	1024	&	$2.45 \cdot 10^4$	&	500	&	--	&	18.58	\\
$10^6$	&	$1.30 \cdot 10^9$	&	1024	&	2048	&	$3.60 \cdot 10^4$	&	500	&	--	&	22.13	\\
$10^7$	&	$1.30 \cdot 10^{10}$	&	2048	&	4096	&	$1.14 \cdot 10^5$	&	200	&	--	&	40.78	\\
\\ \hline \hline \\															
$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64$\times$64	&	$114$	&	100	&	2.42	&	2.42	\\
$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128$\times$128	&	$360$	&	100	&	3.97	&	4	\\
$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256$\times$256	&	$1.14 \cdot 10^3$	&	500	&	6.27	&	6.27	\\
$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512$\times$512	&	$3.60 \cdot 10^3$	&	500	&	9.92	&	9.88	\\
\hline															
\end{tabularx}
\end{center}

>>>>

In this work, we study a method of achieving accelerated evolution of a
convective simulation through adjusting the thermodynamic state using information 
from resolved, convective dynamics. We couple measurements of the (non-converged)
convective solution with knowledge about energy balances in the eventual solution
to self-consistently adjust the mean thermodynamic profile towards its final state. 
While such a method has been used previously \cite{hurlburt&all1986}, 
we find no explanation in the current literature of the steps involved in employing
this method, nor any study into the accuracy of such a method.
In section \ref{sec:experiment}, we describe our convective simulations, our
numerical methods, and our method for achieving accelerated evolution. In
section \ref{sec:results}, we compare solutions reached through the accelerated evolution
method to those that have been evolved through a full diffusive timescale, and we
examine select simulations at very high Ra which have achieved accelerated evolution. Finally,
in section \ref{sec:extensions}, we discuss extensions of the methods presented here,
and we offer concluding remarks.

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/time_trace.png}
\caption{A time trace is shown of kinetic energy (black) and mean temperature (blue)  vs. time 
for an SE run at $S = 10^5$ (a). The mean evolved values of kinetic energy and mean temperature
are denoted by the horizontal dashed black and blue lines. 
By taking an average of the fluxes early in the
simulation (b), and appropriately using the AE method described here, the evolution
of these atmospheres can be greatly accelerated. The time trace of such an accelerated
atmosphere, which uses these methods, is shown in (c).  The y-axes and x-axes are
scaled identically as in (a).  Here, the AE method is used three times, marked by
the numbered arrows. The fluxes averaged over the green region which begins at
the vertical dashed line shortly after AE 3 are shown in (c) are shown
in (d), and they are nearly in the fully evolved state, sampled over a similarly
long region that occurs much later in the simulation in (a).  The difference between
the fluxes in the AE and SE ssolutions is shown in (e), and it is small. The dashed
vertical line in (a) denotes the simulation time at which evolved flux measurements
begin to be taken in (c).
\label{fig:time_trace} }
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/parameter_space_comparison.png}
\caption{Volume- and time-averaged measurements of the Nusselt number, the
RMS Reynolds number, and the mean temperature for AE runs are shown in (a)-(c).
Symbols are located at the mean value of
each measurement, vertical lines represent the standard deviation of the measurement,
which shows natural variation over the
averaging window, and error bars represent the change in the mean value over the averaging window,
such that very large error bars represent solutions which are not fully converged when averaging
begins.
(a) The Nusselt number scales as Ra$^{1/5}$, and above S$\geq 10^{3+2/3}$,
simulations exhibit oscillating plume structures whose heat transport varies over time.  
(b) The RMS Reynolds number, which measures the level of turbulence in the evolved solution, scales as
Ra$^{0.45}$. (c) Temperature, with its value at the upper boundary removed, is shown,
and scales as Ra$^{-1/5}$.
Relative error for (d) Nu, (e) Re, and (f) $T$ are shown between measurements 
taken in AE solutions and SE solutions.
The greyed area of the plot indicates the region in which only AE runs were
carried out due to computational expense. The run at $S = 10^5$ marked as a
black square is examined in more details in Figs. \ref{fig:time_trace},
\ref{fig:temp_comparison}, \& \ref{fig:pdf_comparison}.
\label{fig:parameter_space_comparison} }
\end{figure}

@@

As the AE method primarily serves to adjust the thermodynamic structure of the
solution, we compare the temperature profile attained by AE and SE in 
Fig. \ref{fig:temp_comparison}.  We see that the boundary layer length scale is 
nearly identical in the AE and SE solution (Fig. \ref{fig:temp_comparison}a), but that
the mean temperature in the interior differs by about 0.5\% on average
(Fig. \ref{fig:temp_comparison}b). The probability distribution function of point-by-point
temperature values are compared in Fig. \ref{fig:temp_comparison}c.  We construct
this PDF by interpolating our temperature field onto a regular grid, determing the
frequency distribution of all $T$ values, and then properly normalizing such that
the integral of the PDF is unity.  In addition to the
difference in mode which can be seen in the mean vertical profile, the SE case
has a broader spread of temperature values.  This can likely be attributed to the
slight overstabilization of the temperature profile obtained by the AE method
(as can be seen in Fig. \ref{fig:time_trace}a\&b).  One means of comparing two
probability distributions to determine if they are drawn from the same underlying
sample is through the use of a Kolmogorov-Smirnov (KS) \cite{wall&jenkins2012}.
In general, a KS test must be conducted on independent, uncorrelated data, which
poorly describes the point-by-point values of flow in a fluid simulation. Thus,
we will merely use the KS statistic, the maximum difference
between the cumulative distribution functions (CDFs) of the two sample distributions,
as a numerical method of directly comparing the two PDFs.  For the distributions
shown in Fig. \ref{fig:temp_comparison}b,
we find a KS statistic of 0.495 near the modes, which is very large, and implies that
about half of the data points examined in the AE run are at lower temperature than 
at the SE run. However, as shown in Fig. \ref{fig:temp_comparison}d, aside from the
large difference near the modes, the two CDFs differ by less than one part in a hundred.

\begin{figure}[t]
\includegraphics[width=\textwidth]{./figs/temp_comparison.png}
\caption{Comparisons of the evolved thermodynamic states of an AE and SE run
at $S = 10^{5}$ are shown.  (a) Evolved horizontally- and time-averaged 
temperature profiles, as a function of height.
(b) Probability Distribution Functions (PDFs) and their integrated
Cumulative Distribution Functions (CDFs)
of point-by-point measurements of the temperature field.
(c) The percentage difference between the mean temperature profiles as a function of height.
(d) The value of the Kolmogorov-Smirnov (KS) statistic, or the difference between
the AE and SE CDFs, as a function of temperature.
$T$ is sampled every 0.1 time units for 500 total time units,
and was interpolated onto an evenly spaced grid before sampling.
The difference between the mean profiles is very small O(0.5\%), but this small
difference results in a large difference between the two temperature CDFs near the values
of the temperature mode.  The spread of temperature around the mode, or the fluctuations that
drive convection, are nearly identical between the two runs.
\label{fig:temp_comparison} }
\end{figure}

@@

\section{Extensions \& Conclusion}
\label{sec:extensions}
In this work we have used \RB convection as a test case for the AE method, but we argue that
the true power of this method is in its extensions to more complicated studies.
Such extensions are beyond the scope of this paper, but we will briefly describe
areas in which extensions to the AE method should be explored.
We note that a strength of the AE method is its generality.  One
need only derive the steady-state, horizontally-averaged equations for a given
equation set (e.g., Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}))
and couple that information with knowledge of the boundary conditions
and current dynamics (as described in
section \ref{subsection:ae} and appendix \ref{appendix:recipe}).

One such area in which this method can be applied is to simple studies of
internally heated convection \cite{goluskin2016}.  The simplest of these studies 
examine the incompressible Boussinesq equations, as presented in this work,
but include a constant source term in the energy equation. The evolved convective
state in such internally heated systems includes a flux profile whose value linearly
increases with height, as the volumetric heating requires the convection to carry
more flux towards the top of the domain.  These systems can be straightforwardly
studied using the methods that we examined here, but scaling the profiles derived
in Eqn. (\ref{eqn:bvp_ratios}) by the proper, height-dependent flux.

Studies of stratified convection are likely to gain the most through
developing and employing the AE method.
In many studies of stratified convection, the thermal diffusivity
is inversely proportional to the density \cite{anders&brown2017}. Thus, the
thermal timescale is much larger deep in the atmosphere, where density is high and diffusivity
is very low, than it is near the surface.  As such, runs at similar supercriticalities
but with different degrees of stratification can have thermal timescales which
differ by orders of magnitude.  Fortunately, the AE method is easily adapted to
the simplest stratified, compressible systems.  Rather than studying the total
flux through the system, one must only study the flux in excess of the adiabatic
while constructing the fractions of Eqn. (\ref{eqn:bvp_ratios}).  
Furthermore, in addition to solving for
hydrostatic balance and thermal equilibrium, as in Eqns. (\ref{eqn:bouss_BVP_momentum})
\& (\ref{eqn:bouss_BVP_energy}), it is essential to simultaneously
ensure that mass is conserved.  Thus, additional equations and boundary conditions
must be used to ensure that mass is not created or destroyed,
in a manner similar to how mass appears in equations in stellar structure codes
\cite{paxton&all2011}.

Studies of convection frequently examine paired stable and convecting regions
\cite{hurlburt&all1986, brandenburg&all2005, couston&all2017}.
When the interface between the stable region
and the convecting region is stiff and motions do not cross that interface,
convective motions cannot accelerate the restratification of the stable region.
In fully-convective domains, such as those studied in this work, the thermodynamics evolve
at a more rapid rate than the thermal diffusion time across the domain due to
the help of convective motions.  For example, in Fig. \ref{fig:time_trace}a,
the SE solution is fully converged after $4\cdot 10^3$ frefall time units,
despite the thermal timescale being roughly $10^4$ frefall units.

A final area in which we encourage extensions of this method is in the study of systems
operating in the presence of different thermal boundary conditionss.
We have studied solutions in which we employ mixed thermal boundary conditions,
as in Eqn. (\ref{eqn:bcs}). However, the AE method can be easily applied to fixed-temperature
boundary conditions, as well.  The total evolved flux (F$_{\text{bot}}$)
through the system is not known a priori, but it can be measured using the ratios in
Eqn. (\ref{eqn:bvp_ratios}).  The integrated conductive flux is a constant which
does not change with time due to the fixed temperature jump across the domain.  
Thus, the total flux through the system can be calculated as 
$F_{\text{bot}} = \mathcal{P} / \int f_{\text{cond}} dz$. While easily extensible
to fixed-temperature boundary conditions, we hesitate to use the AE method for 
fixed-flux boundary conditions.  In those systems, there are infinitely many degenerate
solutions to the final temperature profile, and the AE method could advance the
solution into an unrealistic state as a result of an arbitrary user choice on the
temperature profile's offset.

In conclusion, here we have described a method for converging convective simulations using
a method of Accelerated Evolution (AE), and compared it to Standard
Evolution (SE) achieved by running simulations for a thermal timescale.
We have shown that the AE method produces evolved solutions on short timescales
whose dynamics are similar to SE solutions, and we have discussed differences that arise
between the two methods.

We have shown that the AE method is valid at low values of $S$, in which solutions
converge quickly and the thermal timescale is short, but that it is also applicable
at high values of $S$, where SE solutions can take an
intractable amount of time. This shows that the AE method not only progresses
solutions towards the correct evolved state (at high $S$), but that it also does not
remove the simulation from the correct evolved state once such a state is achieved (at low $S$). 
We have studied
the AE method in both 2D and 3D, but have restricted most of our study to 2D flows.
As a result of the AE method depending only on 1D information integrated across
the horizontal dimensions of the atmosphere, we only examine a select small group
of 3D simulations to demonstrate the method's efficacy there in addition to in 2D.

This work serves as a first step towards creating robust methods for
achieving evolved convective solutions at high Ra on short timescales.
In order to study how astrophysical systems change over meaningful
evolutionary timescales, there are two main approaches.  One-dimensional
systems which parameterize dynamics can be quickly evolved over thermal timescales.
However, if the experimenter wants to simultaneously study system evolution
in the presence of realistic convective dynamics, we now know that it is
impossible to avoid the constraints that advective dynamics place on
timestep size \cite{viallet&all2011, viallet&all2013, viallet&all2016}
in both implicit and explicit methods. We must explore other avenues
of evolving the system forward on thermal timescales, and this work aims
as a first step in these explorations.

@@

\appendix
\section{Accelerated Evolution Recipe}
\label{appendix:recipe}
In order to achieve Accelerated Evolution (AE), we pause the Direct Numerical Simulation (DNS)
which is evolving the dynamics of the convection and solve a 1D Boundary Value Problem (BVP)
consisting of Eqns. (\ref{eqn:bouss_BVP_momentum}) \& (\ref{eqn:bouss_BVP_energy}).
After solving this BVP, we adjust the fields being evolved in the DNS appropriately
towards their evolved state, and then we continue running the now-evolved DNS.
There specific steps taken in completing the AE method are as follows:
\begin{enumerate}
\item After the start of the DNS, we wait some time, $t_{\text{transient}}$ after
the convective transient in which the dynamics vigorously break away from the hydrostatic
state.
\item Then, during the DNS, we calculate time averages of the 1D profiles of
$F_{\text{conv}}$, $F_{\text{tot}}$, 
and $\angles{\bm{u} \times \bm{\omega}}_{x,y}$, updating them every timestep.  
To calculate these
averages, we use a trapezoidal-rule integration in time, and then divide by the
total time elapsed over which the average is taken. 
\item We pause the DNS once the averages are sufficiently converged. 
To ensure that an average is converged, at
least some time $t_{\text{min}}$ must have passed since the average was started to
ensure that the full range of convective dynamics are probed, and
the profiles must change by no more than $P$\% on a given timestep.
\item Construct F$_\text{conv, ev}$ and $\xi$ as specified in section \ref{subsection:ae}
from the averaged profiles.
\item Solve the BVP for $\angles{T_1}_{x,y}$ and $\angles{\varpi}_{x,y}$ of the
evolved state.  Set the horizontal average of the current DNS thermodynamic fields
equal to the results of the BVP.
\item Multiply the velocity field and the temperature fluctuations, $T - \angles{T}_{x,y}$,
by $\sqrt{\xi}$ in the DNS to properly reduce the convective flux.
\item Continue running the DNS
\end{enumerate}
We refer to this process as an ``AE BVP solve.''

While the use of a single AE BVP solve rapidly advances the convecting state to
one that is closer to the evolved state, we find that repeating this method 
multiple times is the best way to
ensure that the AE solution is truly converged. For all runs in 2D at $S < 10^5$, we
set $t_{\text{transient}} = 50$, completed an AE BVP solve
with $t_{\text{min}} = 30$ and $P = 0.1$, and then repeated the procedure,
including another wait of $t_{\text{transient}} = 50$ before beginning averages.
For all 3D runs and 2D runs with $S \in [10^5, 10^6]$,
we did a first AE BVP solve with $t_{\text{transient}} = 20$,
$t_{\text{min}} = 20$, and $P = 1$ in order to quickly reach a near-
converged state and vastly increase our timestep size.  After this first solve, 
we completed two AE BVP solves, with $t_{\text{transient}} = 30$,
$t_{\text{min}} = 30$, 
and $P = 0.1$ to get very close to the solution (as in Fig. \ref{fig:time_trace}c).
At very high $S = 10^7$, we ran two AE BVP solves with $t_{\text{min}} = 20$ and
$P = 1$. For the first solve, we set $t_{\text{transient}} = 20$, and for the
second we set $t_{\text{transient}} = 30$. We used fewer solves at this high
value of $S$ in part to reduce the computational expense of the run, and in
part because of how a third BVP generally did not modify the solution hugely
(as in Fig. \ref{fig:time_trace}c).

\section{Table of Runs}
\label{appendix:run_table}
In Table \ref{table:run_parameters} we list key properties of all simulations
conducted in this work.  The supercriticality, Rayleigh number, and resolution
are reported.  We report the simulation run time of the SE solutions and AE
solutions, as well as the amount of time over which average measurements
were taken, in freefall time units.  The volume-averaged Nusselt number of the
AE and SE solutions are shown.
In the upper part of the table, information pertaining to 2D runs is reported,
and below the double horizontal bars we report properties of all
3D runs.

\begin{table}
\caption{Simulation parameters}
\label{table:run_parameters}
\begin{center}
\begin{tabularx}{\textwidth}{ X X X X X X X X X }
\hline															
$S$	&	Ra	&	nz	&	nx, ny	&	$t_{\text{therm}}$	&	$t_{\text{avg}}$	&	Nu$_{\text{SE}}$	&	Nu$_{\text{AE}}$	\\
\hline															
$10^{1/3}$	&	$2.79 \cdot 10^3$	&	32	&	64	&	$52.8$	&	100	&	1.46	&	1.46	\\
$10^{2/3}$	&	$6.01 \cdot 10^3$	&	32	&	64	&	$77.6$	&	100	&	1.95	&	1.95	\\
$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64	&	$114$	&	100	&	2.43	&	2.42	\\
$10^{1 + 1/3}$	&	$2.79 \cdot 10^4$	&	32	&	64	&	$167$	&	100	&	2.54	&	2.54	\\
$10^{1 + 2/3}$	&	$6.01 \cdot 10^4$	&	32	&	64	&	$245$	&	100	&	3.14	&	3.14	\\
$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128	&	$360$	&	100	&	3.8	&	3.8	\\
$10^{2 + 1/3}$	&	$2.79 \cdot 10^5$	&	64	&	128	&	$528$	&	100	&	4.71	&	4.71	\\
$10^{2 + 2/3}$	&	$6.01 \cdot 10^5$	&	64	&	128	&	$776$	&	100	&	5.5	&	5.5	\\
$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256	&	$1.14 \cdot 10^3$	&	200	&	6.4	&	6.33	\\
$10^{3 + 1/3}$	&	$2.79 \cdot 10^6$	&	128	&	256	&	$1.67 \cdot 10^3$	&	500	&	6.87	&	6.95	\\
$10^{3 + 2/3}$	&	$6.01 \cdot 10^6$	&	256	&	512	&	$2.45 \cdot 10^3$	&	500	&	7.54	&	7.59	\\
$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512	&	$3.60 \cdot 10^3$	&	500	&	8.83	&	8.83	\\
$10^{4 + 1/3}$	&	$2.79 \cdot 10^7$	&	256	&	512	&	$5.28 \cdot 10^3$	&	500	&	10.13	&	10.14	\\
$10^{4 + 2/3}$	&	$6.01 \cdot 10^7$	&	256	&	512	&	$7.76 \cdot 10^3$	&	500	&	11.65	&	11.69	\\
$10^5$	&	$1.30 \cdot 10^8$	&	512	&	1024	&	$1.14 \cdot 10^4$	&	500	&	14.02	&	14.18	\\
$10^{5 + 1/3}$	&	$2.79 \cdot 10^8$	&	512	&	1024	&	$1.67 \cdot 10^4$	&	500	&	--	&	16.21	\\
$10^{5 + 2/3}$	&	$6.01 \cdot 10^8$	&	512	&	1024	&	$2.45 \cdot 10^4$	&	500	&	--	&	18.58	\\
$10^6$	&	$1.30 \cdot 10^9$	&	1024	&	2048	&	$3.60 \cdot 10^4$	&	500	&	--	&	22.13	\\
$10^7$	&	$1.30 \cdot 10^{10}$	&	2048	&	4096	&	$1.14 \cdot 10^5$	&	200	&	--	&	40.78	\\
\\ \hline \hline \\															
$10^1$	&	$1.30 \cdot 10^4$	&	32	&	64$\times$64	&	$114$	&	100	&	2.42	&	2.42	\\
$10^2$	&	$1.30 \cdot 10^5$	&	64	&	128$\times$128	&	$360$	&	100	&	3.97	&	4	\\
$10^3$	&	$1.30 \cdot 10^6$	&	128	&	256$\times$256	&	$1.14 \cdot 10^3$	&	500	&	6.27	&	6.27	\\
$10^4$	&	$1.30 \cdot 10^7$	&	256	&	512$\times$512	&	$3.60 \cdot 10^3$	&	500	&	9.92	&	9.88	\\
\hline															
\end{tabularx}
\end{center}
\end{table}
